Impact of Demographics and Skills of the Observer on Visual Statistical Inference

### 2012-09-07 sociology_paper.tex
outline updated

\subsection{Choice of Visual Test Statistic} Discuss the effective feature of visual test statistics \citep{heike:2012}. May present some results from \textit{Distance measure} of visual test statistics \citep{niladri:2012}.
\subsection{Question that Human Observer Faces}
\subsection{Observer Personality}
\subsection{Visual Perception of Human Eye} Discuss the results we have on eye tracking experiment \citep{zhao:2012}.
\subsection{Demographics of Observer}
\subsection{Skills of Observer}

>>>>

\subsection{Choice of Visual Test Statistic} Discuss the effective feature of visual test statistics \citep{heike:2012}. May present some results from \textit{Distance measure} of visual test statistics \citep{niladri:2012}.
\subsection{Question that Human Observer Faces} Discuss the importance of the question the observer needs to answer while evaluating the lineup.
\subsection{Observer Personality}
\subsection{Visual Perception of Human Eye} Discuss the results we have on eye tracking experiment \citep{zhao:2012}.
\subsection{Demographics of Observer}  Age, gender and location of the observer.
\subsection{Skills of Observer} Knowledge about statistical plot as well as education level.
